Supplementary Materials for Differences in the Risk of Grade Retention for Biracial and Monoracial Students in the US, 2010-2019

### 2023-03-13 products/paper/supp_materials.qmd
Add table of CBEG probability by race and grade to address issue #34

```{r}
#| label: create-design
#| eval: false
acs_design <- acs %>%
  as_survey_design(ids = cluster, weights = perwt)
```

@@

@@

```{r desc-stats-ses}
#| label: tbl-desc-stats-ses
#| tbl-cap: Socioeconomic resources by race. Shading indicates biracial group. All results apply survey weights.
#| eval: false
tbl_summary <- acs_design %>%
  group_by(race) %>%
  summarize(fam_inc=survey_mean(family_income, vartype = NULL))

@@

```{r}
#| label: tbl-desc-stats-cult
#| tbl-cap: Cultural resources by race. Shading indicates biracial group. All results apply survey weights.
#| eval: false
tbl_summary <- acs_design %>%
  group_by(race) %>%
  summarize(f_born=round(survey_mean(foreign_born, vartype = NULL), 3)*100,
            father_fb=round(survey_mean(foreign_born_father, 
                                        vartype = NULL), 3)*100,
            mother_fb=round(survey_mean(foreign_born_mother, 
                                        vartype = NULL), 3)*100,
            spk_eng_no=round(survey_mean(spk_eng=="No", vartype = NULL), 3)*100,
            spk_eng_some=round(survey_mean(spk_eng=="Somewhat", 
                                           vartype = NULL), 3)*100,
            spk_eng_yes=round(survey_mean(spk_eng=="Yes", vartype = NULL), 3)*100,
            f_spk_eng_no=round(survey_mean(spk_eng_father=="No", 
                                           vartype = NULL), 3)*100,
            f_spk_eng_some=round(survey_mean(spk_eng_father=="Somewhat", 
                                             vartype = NULL), 3)*100,
            f_spk_eng_yes=round(survey_mean(spk_eng_father=="Yes", 
                                            vartype = NULL), 3)*100,
            m_spk_eng_no=round(survey_mean(spk_eng_mother=="No", 
                                           vartype = NULL), 3)*100,
            m_spk_eng_some=round(survey_mean(spk_eng_mother=="Somewhat", 
                                             vartype = NULL), 3)*100,
            m_spk_eng_yes=round(survey_mean(spk_eng_mother=="Yes", 
                                            vartype = NULL), 3)*100)

>>>>

```{r}
#| label: create-design
acs_design <- acs %>%
  as_survey_design(ids = cluster, weights = perwt)
```

@@

```{r prob-race-grade, fig.cap=""}
#| label: tbl-prob-race-grade
#| tbl-cap: Probability of being clearly behind expected grade by race and current grade.
tbl_race_grade <- acs_design %>%
  group_by(race, current_grade) %>%
  summarize(held_back=survey_mean(below_exp_grade, vartype=NULL)) %>%
  ungroup() %>%
  pivot_wider(id_cols=race, names_from=current_grade, 
              values_from=held_back) %>%
  rename(Race=race) %>%
  mutate(K=percent(K, accuracy=0.01),
         `1st`=percent(`1st`, accuracy=0.01),
         `2nd`=percent(`2nd`, accuracy=0.01),
         `3rd`=percent(`3rd`, accuracy=0.01),
         `4th`=percent(`4th`, accuracy=0.01),
         `5th`=percent(`5th`, accuracy=0.01),
         `6th`=percent(`6th`, accuracy=0.01),
         `7th`=percent(`7th`, accuracy=0.01),
         `8th`=percent(`8th`, accuracy=0.01),
         `9th`=percent(`9th`, accuracy=0.01),
         `10th`=percent(`10th`, accuracy=0.01),
         `11th`=percent(`11th`, accuracy=0.01),
         `12th`=percent(`12th`, accuracy=0.01))

tbl_race_grade %>%
  kbl(booktabs = TRUE,
      linesep = NULL,
      align = c("l",rep("r", ncol(tbl_race_grade)-1))) %>%
  kable_styling(font_size=8) %>%
  column_spec(2:14, width = "0.6cm")
```

@@

```{r desc-stats-ses}
#| label: tbl-desc-stats-ses
#| tbl-cap: Socioeconomic resources by race. Shading indicates biracial group. All results apply survey weights.
tbl_summary <- acs_design %>%
  group_by(race) %>%
  summarize(fam_inc=survey_mean(family_income, vartype = NULL))

@@

```{r}
#| label: tbl-desc-stats-cult
#| tbl-cap: Cultural resources by race. Shading indicates biracial group. All results apply survey weights.
tbl_summary <- acs_design %>%
  group_by(race) %>%
  summarize(f_born=round(survey_mean(foreign_born, vartype = NULL), 3)*100,
            father_fb=round(survey_mean(foreign_born_father, 
                                        vartype = NULL), 3)*100,
            mother_fb=round(survey_mean(foreign_born_mother, 
                                        vartype = NULL), 3)*100,
            spk_eng_no=round(survey_mean(spk_eng=="No", vartype = NULL), 3)*100,
            spk_eng_some=round(survey_mean(spk_eng=="Somewhat", 
                                           vartype = NULL), 3)*100,
            spk_eng_yes=round(survey_mean(spk_eng=="Yes", vartype = NULL), 3)*100,
            f_spk_eng_no=round(survey_mean(spk_eng_father=="No", 
                                           vartype = NULL), 3)*100,
            f_spk_eng_some=round(survey_mean(spk_eng_father=="Somewhat", 
                                             vartype = NULL), 3)*100,
            f_spk_eng_yes=round(survey_mean(spk_eng_father=="Yes", 
                                            vartype = NULL), 3)*100,
            m_spk_eng_no=round(survey_mean(spk_eng_mother=="No", 
                                           vartype = NULL), 3)*100,
            m_spk_eng_some=round(survey_mean(spk_eng_mother=="Somewhat", 
                                             vartype = NULL), 3)*100,
            m_spk_eng_yes=round(survey_mean(spk_eng_mother=="Yes", 
                                            vartype = NULL), 3)*100)
